\section{Introduction}
% no \IEEEPARstart
%Present topic - uses of drones in reality context, chosen because it is a control challenge, rather than revolutionary.
In the last years, the interest for quadcopters has increased due to the multiple possibilities they offer. Among these, the most well-known ones are search and rescue missions in difficult environments, inspection of big structures and surveillance. \nolinebreak\cite{droneuses}

The quadcopter constitutes a control challenge due to its unstable nature and coupled behavior. The system has six degrees of freedom, the three position coordinates and the three orientations, and there are only four actuation variables, namely the motor rotational speeds. \cite{draganflyer}% \fxnote{Explain "coupled" ???}\fxnote{What is the source about?}

%Previous Approaches - examples of what others have done to obtain similar goals of stabilization like we pursue. What have others done differently than we plan to do to obtain the same end result.
The control of a quadcopter has been addressed many times in the recent years. In Mian et al. \cite{backstepping} the quadcopter is controlled using a back-stepping technique and non-linear controllers. Another way of solving the issue is presented in Tayebi et al. \cite{quaternionsPD} in which the quadcopter attitude is modeled using quaternions and controlled with a PD based controller. In \cite{MianWang} Mian and Wang model the system using its dynamic equations and use non-linear controllers to achieve a steady flight while in Mokhtari et al. \cite{GHinf} the system is controlled by a mixture of a robust feedback linearization and a modified optimization control method.

%Describe our approach shortly.
%\fxnote{Why we do not include specific details of our hardware or our network in the methods??}
%\fxnote{Explain a bit what we want to do in the paper: See how these methods can stabilize a quadcopter ...}
%\fxnote{What you can consider to say is that you want to see if it is possible to use a linear control scheme with cascaded control to stabilize the attitude and position using networked distribution of sensors.}
This paper addresses the performance achievable using a state space design strategy for the attitude control combined with a cascaded structure with classical linear translational controllers. Furthermore, the influence of remote sensing and the influence of the attitude controller bandwidth on the translational controllers are considered.
%
%The approach presented here tries to control the attitude and translational position of the quadcopter using linear controllers and transmitting sensor data through a wireless network. 

In \autoref{sec:model}, the model of the quadcopter is obtained by a first principles method. This approach yields a non-linear model that describes the attitude and translational behavior of the quadcopter. The model is then linearized around an equilibrium point, which is the hovering position. 
%
With the linearized equations, controllers for attitude and translational behaviors are designed in \autoref{sec:control}. The attitude controller is obtained by means of a state space representation while the translational controller is designed using classical control. In the control system, the translational constitutes an outer loop and sets the reference for the attitude controller.
%
Since the sensors are not placed on the quadcopter and the information comes from an external motion tracking system \cite{vicon}, an analysis on how the network affects the control loop is also presented, this is described in \autoref{sec:network}.
%
In \autoref{sec:results}, the simulations and experimental results of the designed controllers are presented and hereafter they are discussed in \autoref{sec:discussion}. Lastly, a conclusion is presented in \autoref{sec:conclusion} and possible future work is mentioned in \autoref{sec:futurework}. %\fxnote{Are we to present both simulation and real results?}