\newgeometry{left=25mm,	right=25mm, top=18mm}

\chapter*{Preface}
%\textbf{\huge{Preface}}
This first semester project of the Control and Automation Master's Program at Aalborg University has been carried out in the fall 2016 by the student group 16gr733. This project has been supervised by Anders la Cour-Harbo, associate professor at Aalborg University.

The focus of this project has been to design an attitude and position control for a quadcopter in a networked distributed system. 

It is expected of the reader to have an engineering level knowledge within mathematics and physics as well as electronics and linear control theory.

For referencing sources the standard ISO 690 is used, noted as [n], where n represents a number in the bibliography. The bibliography is placed at the end of the worksheets, before the appendices. Additional attachments are uploaded along with the worksheets, these are code-files, MATLAB simulation scrips, sources and the documents submitted to SEMCON.

Special thanks to Henrik Schiøler, associated professor at Aalborg University, for providing the quadcopter, his assistance in the laboratory and kind sharing of experience. Thanks as well to Jesper D. Pedersen, engineering worker at Aalborg University, for building test setups for the quadcopter. 

%A thank should be given to Anders la Cour-Harbo, associate professor at Aalborg University, who has been the supervisor of the project. 
%
%Thank given to Jesper D. Pedersen, industrial technician at Aalborg University, for building test setups for the quadcopter. 
%
%Lastly Henrik Shiøler, associated professor at Aalborg University, must be acknowledge for providing the quadcopter, his assistance in the laboratory and kind sharing of implementation experience.


\textbf{Text by:}\\
\vspace{-5pt}
\begin{table}[H]
	\centering
		\begin{tabular}{c c c}
			\underline{\phantom{JAERJAERJAERJAERGO}} & \phantom{cookies} & \underline{\phantom{JAERJAERJAERJAERGO}} \\
			Alejandro Alonso García			& \phantom{cookies} & Amalie Vistoft Petersen		\\
			&&\\
			\underline{\phantom{JAERJAERJAERJAERGO}} & \phantom{cookies} & \underline{\phantom{JAERJAERJAERJAERGO}} \\
			Andrea Victoria Tram Løvemærke			& \phantom{cookies} & Niels Skov Vestergaard		\\
			&&\\
	    \multicolumn{3}{c}{\underline{\phantom{JAERJAERJAERJAERGO}}}\\
	    \multicolumn{3}{c}{Noelia Villarmarzo Arruñada}\\				
		\end{tabular}
\end{table}

\pagebreak
\restoregeometry