\section{Project scope}

In this section the scope of the project will be described with the purpose of giving the reader an overview. \newpar

This project's main purpose is to make the stabilisation of a quadcopter, that will allow it to hower steadily. It must also be able to move in all three dimensions when given a location input from a grounded user interface. \\
The project will use Vicon, a motion tracking system, that will allow the quadcopter to recive precise data of its position and orientation. 
As the main focus in this project is the stabilization of an airborn object, the quadcopter will first be using the Vicon data for both orientation and position. When this is fully functioning, the orientation data must instead come from on board sensors. This is done, as hardware work must not be of too high priority compared to controlling the quadcopter. \newpar

The microcontoller that will handle the on-board control is an AtMega2560. Its IOS is FreeRTOS and it is programmed in C. 


In this section the scope of the project will be described. The purpose is to give the reader an overview of the project. \newpar

The project's main purpose is to stabilize a quadcopter. This means that the quadcopter is able to hower and manoeuvre steadily without making visible oscillation like movements while flying, i.e. shaking. The quadcopter should therefore be able to move in all three dimensions when given a specific position from a ground station. \\
In this project a motion tracking system called Vicon is utilized. Vicon is able to gather the quadcopter position and orientation, thereby making it possible to utilize the Vicon data when controlling the quadcopter. 
As the main focus in this project is the stabilization of a quadcopter, the Vicon data will be utilized first for both orientation and position of the quadcopter. When this is fully functioning, the orientation data could instead come from on board sensors. This will not be prioritised as hardware is not set as a high priority in the project compared to controlling and stabilization of the quadcopter. \newpar

The microcontroller which handles the on-board control is an AtMega2560. The internal operating system utilized is FreeRTOS and C is used as the programming language.